\Large\bf FlexibleSUSY 2.0: Extensions to investigate the phenomenology of SUSY and non-SUSY models

### 2019-03-18 doc/Manuals/flexiblesusy-2.0.tex
start tidying up doc directory

The 2-loop and 3-loop Higgs mass contributions from above can be
enabled at runtime by setting the following flags in the SLHA input
file:
%
\begin{lstlisting}
Block FlexibleSUSY
    4   3         # pole mass loop order
    5   3         # EWSB loop order
    7   2         # threshold corrections loop order
    8   1         # Higgs 2-loop corrections O(alpha_t alpha_s)
   10   1         # Higgs 2-loop corrections O(alpha_t^2)
   24   122111221 # individual threshold correction loop orders
   26   1         # Higgs 3-loop corrections O(alpha_t alpha_s^2)
   28   1         # Higgs 3-loop corrections O(alpha_t^2 alpha_s)
   29   1         # Higgs 3-loop corrections O(alpha_t^3)
\end{lstlisting}
%
In \fs's \mathematica interface, the above SLHA configuration options
correspond to
%
\begin{lstlisting}[language=Mathematica]
handle = FS<model>OpenHandle[
    fsSettings -> {poleMassLoopOrder -> 3,
                   ewsbLoopOrder -> 3,
                   thresholdCorrectionsLoopOrder -> 2,
                   higgs2loopCorrectionAtAs -> 1,
                   higgs2loopCorrectionAtAt -> 1,
                   thresholdCorrections -> 122111221,
                   higgs3loopCorrectionAtAsAs -> 1,
                   higgs3loopCorrectionAtAtAs -> 1,
                   higgs3loopCorrectionAtAtAt -> 1}
    ...];
\end{lstlisting}
%
See \appref{app:fs_config_options} for a list and description of
all of \fs's configuration options.
%
In \figref{fig:SM_thresholds} the impact of the leading 3-loop
Standard Model corrections of $O(\at^3 + \at^2 \as + \at \as^2)$ on
the light \CP-even Higgs pole mass in the MSSM in the pure effective
field theory (EFT) calculation of \HSSUSY is shown with the red
dashed-dotted line.  The line shows the predicted 3-loop Higgs mass
relative to the one calculated at the 2-loop level as a function of
the SUSY scale \MS, by taking into account the 1-loop threshold
correction for $\as^{\SM}(M_Z)$ and the 2-loop QCD correction to
$y_t^{\SM}(M_Z)$.  We find that the explicit 3-loop Standard Model
contributions to the Higgs mass lead to a small positive shift by
around $30\unit{MeV}$.
%
\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.5\textwidth]{doc/plots/HSSUSY/HSSUSY_thresholds}
  \caption{Effect of different SM corrections on the Higgs
    pole mass in the pure EFT calculation of \HSSUSY for
    $\tan\beta = 5$ and $X_t = \sqrt{6}\MS$ as a function of the SUSY
    scale \MS.  The orange band marks the region where \HSSUSY
    predicts a Higgs mass compatible with the experimental value of
    $(125.09 \pm 0.32)\unit{GeV}$ \cite{Aad:2015zhl}.}
  \label{fig:SM_thresholds}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.49\textwidth]{doc/plots/Himalaya/scan_Mh_MS_TB-5_Xt-0}\hfill
  \includegraphics[width=0.49\textwidth]{doc/plots/Himalaya/scan_Mh_MS_TB-5_Xt-0_delta_alpha}\\
  \includegraphics[width=0.49\textwidth]{doc/plots/Himalaya/scan_Mh_Xt_TB-5_MS-2000}\hfill
  \includegraphics[width=0.49\textwidth]{doc/plots/Himalaya/scan_Mh_Xt_TB-5_MS-2000_delta_alpha}
  \caption{Comparison of different 2-loop and 3-loop calculations of
    the lightest \CP-even Higgs mass in the MSSM with different \fs
    spectrum generators for $\tan\beta = 5$.  In the top row we set
    $X_t = 0$ and in the bottom row we use $\MS = 2\unit{TeV}$.}
  \label{fig:Mh-himalaya}
\end{figure}
%
\figref{fig:Mh-himalaya} shows a comparison of the different light
\CP-even Higgs mass calculations available in \fs.  The scenario is
chosen such that all soft-breaking \DRbar mass parameters, the
superpotential
$\mu$ parameter and the \DRbar \CP-odd Higgs mass are equal to the SUSY
scale $\MS$ at the scale $Q =
\MS$ and all \DRbar sfermion mixing parameters
$X_f$ are set to zero, except for the stop mixing parameter
$X_t$.  Furthermore, we set $M_t =
173.34\unit{GeV}$, $\as^{\SM(5)}(M_Z) =
0.1184$ and $\aem^{\SM(5)}(M_Z) =
1/127.944$.  The top row of \figref{fig:Mh-himalaya} shows the Higgs
mass as a function of $\MS$ for $X_t = 0$ and $\tan\beta =
5$.  In the left panel of the top row the classic 2-loop fixed-order
calculation with \fs \cite{Athron:2014yba} is shown as the blue dashed
line and the pure EFT calculation with \HSSUSY is shown as the black
dotted line.  The reason why these two curves do not deviate from each
other logarithmically when
$\MS$ increases is an accidental cancellation of large
logarithmic contributions in the fixed-order calculation
\cite{Athron:2016fuq}.  The green dashed-dotted line shows the
improved version of the \feft calculation \cite{Athron:2016fuq}, which
interpolates
between the fixed-order calculation at low \MS and the pure EFT
calculation at large \MS.  See \secref{sec:feft} for a discussion of
the improvements of \feft.  The red solid line shows the 3-loop
calculation up to $O(\at\as^2 +
\ab\as^2)$ with \fsh \cite{Harlander:2017kuc}.  In this calculation, the
full 2-loop \SQCD contributions to the \DRbar top and bottom Yukawa
couplings $y_{t,b}(M_Z)$ \cite{Bednyakov:2007vm,Bednyakov:2002sf,Bednyakov:2005kt}
are taken into account.  The sum of these contributions
and the explicit 3-loop contribution to the \CP-even
Higgs mass matrix leads to a downward shift of the predicted Higgs
mass by $1$--$2\unit{GeV}$, depending on \MS, compared to the classic 2-loop
calculation with \fs (blue dashed line).  As also discussed in
Ref.~\cite{Harlander:2017kuc}, this brings the prediction closer to the pure
EFT calculation, which is expected to lead to a more precise result above
the TeV scale.  In the left panel of the bottom row of
\figref{fig:Mh-himalaya}, the calculated Higgs mass is shown as a
function of the stop mixing parameter $X_t$ for fixed
$\MS = 2\unit{TeV}$.  Also for non-zero
$X_t$, one finds a reduction of the Higgs mass by
$1$--$3\unit{GeV}$, which brings the prediction closer to the one of
the pure EFT calculation.

@@

\paragraph{2-loop \SQCD corrections to the \DRbar top and bottom Yukawa couplings in the MSSM}
In the MSSM, the full 2-loop \SQCD corrections of $O(\as^2)$
to the \DRbar top Yukawa coupling
\cite{Bednyakov:2007vm,Bednyakov:2002sf,Bednyakov:2005kt} as well as
the 2-loop \SQCD $O(\as^2)$ and partial electroweak contributions
to the \DRbar bottom Yukawa coupling \cite{Bednyakov:2009wt} are
known.  These 2-loop corrections have already been made available in
\softsusy~3.7.0 \cite{Allanach:2014nba}.  The 2-loop \SQCD
corrections of $O(\as^2)$ are now also incorporated in \fstwo and can be
used by setting the following switch in the model file:\footnote{We
  kindly thank Alexander Bednyakov for providing the 2-loop \SQCD
  expressions.}
%
\begin{lstlisting}
UseMSSMYukawa2Loop = True;
\end{lstlisting}
%
To take these 2-loop contributions into account at runtime, the
following flags should also be set in the SLHA input file:
%
\begin{lstlisting}
Block FlexibleSUSY
    7   2         # threshold corrections loop order
   24   122111221 # individual threshold correction loop orders
\end{lstlisting}
%
In \fs's \mathematica interface, the above SLHA configuration options
correspond to
%
\begin{lstlisting}[language=Mathematica]
handle = FS<model>OpenHandle[
    fsSettings -> {thresholdCorrectionsLoopOrder -> 2,
                   thresholdCorrections -> 122111221}
    ...];
\end{lstlisting}
%
In \figref{fig:MSSMMuBMu} we show in blue the effect of the full
2-loop \SQCD corrections on the lightest \CP-even Higgs pole mass in
the MSSM\@.  The blue dashed line shows the effect in \fstwo and the
crosses in \softsusy~4.0.1.
As can be seen from the figure, the full 2-loop \SQCD corrections are
negative and can affect the Higgs mass by several GeV, as has been
observed in Ref.~\cite{Allanach:2014nba}.  In the left panel of
\figref{fig:MSSMMuBMu}, the shift in the Higgs mass is shown as a
function of the SUSY scale.  For scales above $\approx 2\unit{TeV}$ we
find a logarithmic shift in $M_h$, which is caused by new large
logarithms originating from the 2-loop contribution of the SUSY
particles to the \DRbar top Yukawa coupling.  We also find that these
new logarithms alone would spoil the accidental cancellation of large
logarithms described in Ref.~\cite{Athron:2016fuq}.
%
Note that in the MSSM the effect of the 2-loop \SQCD corrections to
the top and bottom Yukawa couplings is a partial 3-loop contribution
to the light \CP-even Higgs pole mass.  Thus, these 2-loop \SQCD corrections
must be taken into account if the explicit 3-loop Higgs mass
contributions of $O(\at \as^2 + \ab \as^2)$ from
\Himalaya are used, see above.
%
\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.49\textwidth]{doc/plots/MSSMMuBMu/scan_MSSMMuBMu_Mh_MS_TB-5_Xt-0}\hfill
  \includegraphics[width=0.49\textwidth]{doc/plots/MSSMMuBMu/scan_MSSMMuBMu_Mh_Xt_TB-5_MS-2000}
  \caption{Effect of the 3-loop RGEs for all MSSM parameters (red),
    2-loop \SQCD contributions to $y_b$ and $y_t$ (blue) and 2-loop
    \SQCD contributions to $\as$ (green) on the lightest \CP-even
    Higgs pole mass in the MSSM\@.  The lines show the shift in the
    Higgs pole mass in \fstwo compared to the one obtained with 2-loop
    RGEs, full 1-loop \SQCD + 2-loop SM-QCD contributions to $y_t$ and
    1-loop \SQCD contributions to $\as$.  The crosses show the
    corresponding shift obtained with \softsusy~4.0.1.  In the left
    panel we use $\tan\beta = 5$ and $X_t = 0$ and in the right panel
    we fix $\tan\beta = 5$ and $\MS = 2\unit{TeV}$.}
  \label{fig:MSSMMuBMu}
\end{figure}

@@

SUSYScaleInput = {
    {M122, MAInput^2 Sin[ArcTan[v2/v1]] Cos[ArcTan[v2/v1]]},
    FSSolveEWSBFor[EWSBOutputParameters]
};
\end{lstlisting}
%
Finally, we need to fix the quartic Higgs couplings of the \THDMII at
the scale $\MS$.  The necessary relations between the MSSM parameters
and the quartic Higgs couplings of the \THDMII are known at the full
1-loop and leading 2-loop level
\cite{Haber:1993an,Gorbahn:2009pp,Lee:2015uza}.
We can use expressions from these references to write the boundary conditions
on the quartic Higgs couplings at the SUSY scale,
shown in lines 23--57 of \appref{app:THDMIIMSSMBC},
in terms of the 1- and 2-loop threshold corrections,
shown in lines 110--398 of the same listing
which displays the complete
\fs model file.
\figref{fig:THDMIIMSSMBC_Mh_MS} shows the lightest \CP-even
Higgs pole mass calculated at the 1-loop level with \fs in this EFT
setup as a function of $\tan\beta^{\THDMII}(M_t)$ and $\MS$ for
$m_A^{\THDMII}(\MEWSB) = 200\unit{GeV}$, $\MEWSB = M_t$ and maximal
stop mixing.  The figure shows that using this setup, \fs can reproduce
the results presented in the left panels of Figure~2 of
Ref.~\cite{Lee:2015uza}.  This EFT model is
distributed with the \fs package under the name \modelname{THDMIIMSSMBC}.
%
\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.49\textwidth]{doc/plots/THDMIIMSSMBC/THDMIIMSSMBC_Mh_MS_TB_MA-200_Xt-0}\hfill
  \includegraphics[width=0.49\textwidth]{doc/plots/THDMIIMSSMBC/THDMIIMSSMBC_Mh_MS_TB_MA-200_Xt-sqrt6}
  \caption{Lightest \CP-even Higgs pole mass calculated at the 1-loop
    level in the effective \THDM setup as a function of $\tan\beta$ and
    $\MS$ for $m_A(M_t) = 200\unit{GeV}$, $A_t = \mu/\tan\beta +
    X_t$, $A_b = A_\tau = A_t$, $\mu = \MS$, $M_t = 173.34\unit{GeV}$
    and $\as^{\SM(5)}(M_Z) = 0.1184$.  The left panel shows the results for $X_t
    = 0$ and the right panel for $X_t = \sqrt{6}\MS$.  The solid line
    corresponds to a Higgs pole mass of $125\unit{GeV}$ and the dashed
    lines to $124\unit{GeV}$ and $126\unit{GeV}$, respectively.}
  \label{fig:THDMIIMSSMBC_Mh_MS}
\end{figure}

@@

...
\end{lstlisting}
%
The full expressions for the threshold corrections can be found in the
\HSSUSY model file.  In addition, \HSSUSY makes use of the known
3-loop SM $\beta$ functions, 3-loop corrections to the
running top Yukawa coupling, 3-loop threshold corrections to the
strong coupling and up to 3-loop corrections to the Higgs pole mass:
%
\begin{lstlisting}
UseSM3LoopRGEs    = True; (* 3-loop RGEs *)
UseYukawa3LoopQCD = True; (* 3-loop thresholds for yt *)
UseSMAlphaS3Loop  = True; (* 3-loop thresholds for alpha_s *)
UseHiggs2LoopSM   = True; (* 2-loop contributions to Mh *)
UseHiggs3LoopSM   = True; (* 3-loop contributions to Mh *)
\end{lstlisting}
%
With all these corrections enabled, \HSSUSY can be regarded as an
improved variant of \susyhd \cite{Vega:2015fna}, the difference being
that \HSSUSY includes generalized 2-loop threshold corrections also
involving $\ab$ and $\atau$, which are not present in \susyhd.  In
\secref{sec:feft}, \HSSUSY is also compared to the fixed-order
calculation in the full MSSM as well as to \feft.  The following
Examples \ref{ex:HSSUSY_parallel}--\ref{ex:HSSUSY_EFT_uncertainty}
show how \HSSUSY can be run and how different sources of uncertainty
can be estimated.\footnote{The example scripts can be found in the
  \code{doc/examples-2.0/} sub-directory of the \fs package.}
%
\begin{example}[label=ex:HSSUSY_parallel]
  For illustration, we show in this example the Higgs mass prediction
  in the MSSM with \HSSUSY.  In the following example script, a scan
  over the relative \DRbar stop mixing parameter $X_t/\MS$ is performed for
  $\tan\beta(\MS) = 5$ and three different values of the SUSY scale $\MS$.
  This is done in parallel on all available CPU cores.
  %
\begin{lstlisting}
Get["models/HSSUSY/HSSUSY_librarylink.m"];

@@

data = {
    ParallelMap[{#, CalcMh[5, #, 1000 ]}&, Range[-3.5, 3.5, 0.1]],
    ParallelMap[{#, CalcMh[5, #, 2000 ]}&, Range[-3.5, 3.5, 0.1]],
    ParallelMap[{#, CalcMh[5, #, 10000]}&, Range[-3.5, 3.5, 0.1]]
};
\end{lstlisting}%$
%
When plotting this data, the following figure results:
%
\begin{center}
  \includegraphics[width=0.5\textwidth]{doc/plots/HSSUSY/Mh_Xt}
\end{center}
\end{example}

@@

data = {
    ParallelMap[{#, CalcDMh[1000 , 5, #]}&, Range[-3.5, 3.5, 0.1]],
    ParallelMap[{#, CalcDMh[2000 , 5, #]}&, Range[-3.5, 3.5, 0.1]],
    ParallelMap[{#, CalcDMh[10000, 5, #]}&, Range[-3.5, 3.5, 0.1]]
};
\end{lstlisting}%$
%
In the function \code{CalcDMh[]}, the three sources of uncertainty are
combined linearly.  When drawing the uncertainty $\Delta
M_h^{\SM}$, estimated in this way, around the central value as $M_h
\pm \Delta M_h^{\SM}$, the following figure results:
\begin{center}
  \includegraphics[width=0.5\textwidth]{doc/plots/HSSUSY/Mh_Xt_uncertainty}
\end{center}
%
We find that the uncertainty $\Delta
M_h^{\SM}$ is around or below $500\unit{MeV}$.
\end{example}

@@

data = ParallelMap[{#, Sequence @@ CalcDMh[#, 5, Sqrt[6]]}&,
                   LogRange[173.34, 10^5, 60]];
\end{lstlisting}%$
%
In the function \code{CalcDMh[]}, the difference between the Higgs masses
calculated with $\texttt{DeltaEFT} = 0$ and $\texttt{DeltaEFT} =
1$ is used as the uncertainty estimate ($\texttt{DeltaEFT} =
0$ corresponds to the standard \HSSUSY calculation).  When drawing the
uncertainty estimated in this way symmetrically around the central
value, the following figure results:
%
\begin{center}
  \includegraphics[width=0.5\textwidth]{doc/plots/HSSUSY/Mh_MS_EFT_uncertainty}
\end{center}
%
As expected, we find that the ``EFT uncertainty'' decreases as
$\MS$ increases and falls below $150\unit{MeV}$ for $\MS \gtrsim 2\unit{TeV}$.
\end{example}

@@

    doc/plots/CMSSM_solution_regions/CMSSM_solution_regions}

@@

    doc/plots/CMSSM_solution_regions/CMSSM_higgs_mass}

>>>>

The 2-loop and 3-loop Higgs mass contributions from above can be
enabled at runtime by setting the following flags in the SLHA input
file:
%
\begin{lstlisting}
Block FlexibleSUSY
    4   3         # pole mass loop order
    5   3         # EWSB loop order
    7   2         # threshold corrections loop order
    8   1         # Higgs 2-loop corrections O(alpha_t alpha_s)
   10   1         # Higgs 2-loop corrections O(alpha_t^2)
   24   122111221 # individual threshold correction loop orders
   26   1         # Higgs 3-loop corrections O(alpha_t alpha_s^2)
   28   1         # Higgs 3-loop corrections O(alpha_t^2 alpha_s)
   29   1         # Higgs 3-loop corrections O(alpha_t^3)
\end{lstlisting}
%
In \fs's \mathematica interface, the above SLHA configuration options
correspond to
%
\begin{lstlisting}[language=Mathematica]
handle = FS<model>OpenHandle[
    fsSettings -> {poleMassLoopOrder -> 3,
                   ewsbLoopOrder -> 3,
                   thresholdCorrectionsLoopOrder -> 2,
                   higgs2loopCorrectionAtAs -> 1,
                   higgs2loopCorrectionAtAt -> 1,
                   thresholdCorrections -> 122111221,
                   higgs3loopCorrectionAtAsAs -> 1,
                   higgs3loopCorrectionAtAtAs -> 1,
                   higgs3loopCorrectionAtAtAt -> 1}
    ...];
\end{lstlisting}
%
See \appref{app:fs_config_options} for a list and description of
all of \fs's configuration options.
%
In \figref{fig:SM_thresholds} the impact of the leading 3-loop
Standard Model corrections of $O(\at^3 + \at^2 \as + \at \as^2)$ on
the light \CP-even Higgs pole mass in the MSSM in the pure effective
field theory (EFT) calculation of \HSSUSY is shown with the red
dashed-dotted line.  The line shows the predicted 3-loop Higgs mass
relative to the one calculated at the 2-loop level as a function of
the SUSY scale \MS, by taking into account the 1-loop threshold
correction for $\as^{\SM}(M_Z)$ and the 2-loop QCD correction to
$y_t^{\SM}(M_Z)$.  We find that the explicit 3-loop Standard Model
contributions to the Higgs mass lead to a small positive shift by
around $30\unit{MeV}$.
%
\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.5\textwidth]{doc/Manuals/plots/HSSUSY/HSSUSY_thresholds}
  \caption{Effect of different SM corrections on the Higgs
    pole mass in the pure EFT calculation of \HSSUSY for
    $\tan\beta = 5$ and $X_t = \sqrt{6}\MS$ as a function of the SUSY
    scale \MS.  The orange band marks the region where \HSSUSY
    predicts a Higgs mass compatible with the experimental value of
    $(125.09 \pm 0.32)\unit{GeV}$ \cite{Aad:2015zhl}.}
  \label{fig:SM_thresholds}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.49\textwidth]{doc/Manuals/plots/Himalaya/scan_Mh_MS_TB-5_Xt-0}\hfill
  \includegraphics[width=0.49\textwidth]{doc/Manuals/plots/Himalaya/scan_Mh_MS_TB-5_Xt-0_delta_alpha}\\
  \includegraphics[width=0.49\textwidth]{doc/Manuals/plots/Himalaya/scan_Mh_Xt_TB-5_MS-2000}\hfill
  \includegraphics[width=0.49\textwidth]{doc/Manuals/plots/Himalaya/scan_Mh_Xt_TB-5_MS-2000_delta_alpha}
  \caption{Comparison of different 2-loop and 3-loop calculations of
    the lightest \CP-even Higgs mass in the MSSM with different \fs
    spectrum generators for $\tan\beta = 5$.  In the top row we set
    $X_t = 0$ and in the bottom row we use $\MS = 2\unit{TeV}$.}
  \label{fig:Mh-himalaya}
\end{figure}
%
\figref{fig:Mh-himalaya} shows a comparison of the different light
\CP-even Higgs mass calculations available in \fs.  The scenario is
chosen such that all soft-breaking \DRbar mass parameters, the
superpotential
$\mu$ parameter and the \DRbar \CP-odd Higgs mass are equal to the SUSY
scale $\MS$ at the scale $Q =
\MS$ and all \DRbar sfermion mixing parameters
$X_f$ are set to zero, except for the stop mixing parameter
$X_t$.  Furthermore, we set $M_t =
173.34\unit{GeV}$, $\as^{\SM(5)}(M_Z) =
0.1184$ and $\aem^{\SM(5)}(M_Z) =
1/127.944$.  The top row of \figref{fig:Mh-himalaya} shows the Higgs
mass as a function of $\MS$ for $X_t = 0$ and $\tan\beta =
5$.  In the left panel of the top row the classic 2-loop fixed-order
calculation with \fs \cite{Athron:2014yba} is shown as the blue dashed
line and the pure EFT calculation with \HSSUSY is shown as the black
dotted line.  The reason why these two curves do not deviate from each
other logarithmically when
$\MS$ increases is an accidental cancellation of large
logarithmic contributions in the fixed-order calculation
\cite{Athron:2016fuq}.  The green dashed-dotted line shows the
improved version of the \feft calculation \cite{Athron:2016fuq}, which
interpolates
between the fixed-order calculation at low \MS and the pure EFT
calculation at large \MS.  See \secref{sec:feft} for a discussion of
the improvements of \feft.  The red solid line shows the 3-loop
calculation up to $O(\at\as^2 +
\ab\as^2)$ with \fsh \cite{Harlander:2017kuc}.  In this calculation, the
full 2-loop \SQCD contributions to the \DRbar top and bottom Yukawa
couplings $y_{t,b}(M_Z)$ \cite{Bednyakov:2007vm,Bednyakov:2002sf,Bednyakov:2005kt}
are taken into account.  The sum of these contributions
and the explicit 3-loop contribution to the \CP-even
Higgs mass matrix leads to a downward shift of the predicted Higgs
mass by $1$--$2\unit{GeV}$, depending on \MS, compared to the classic 2-loop
calculation with \fs (blue dashed line).  As also discussed in
Ref.~\cite{Harlander:2017kuc}, this brings the prediction closer to the pure
EFT calculation, which is expected to lead to a more precise result above
the TeV scale.  In the left panel of the bottom row of
\figref{fig:Mh-himalaya}, the calculated Higgs mass is shown as a
function of the stop mixing parameter $X_t$ for fixed
$\MS = 2\unit{TeV}$.  Also for non-zero
$X_t$, one finds a reduction of the Higgs mass by
$1$--$3\unit{GeV}$, which brings the prediction closer to the one of
the pure EFT calculation.

@@

\paragraph{2-loop \SQCD corrections to the \DRbar top and bottom Yukawa couplings in the MSSM}
In the MSSM, the full 2-loop \SQCD corrections of $O(\as^2)$
to the \DRbar top Yukawa coupling
\cite{Bednyakov:2007vm,Bednyakov:2002sf,Bednyakov:2005kt} as well as
the 2-loop \SQCD $O(\as^2)$ and partial electroweak contributions
to the \DRbar bottom Yukawa coupling \cite{Bednyakov:2009wt} are
known.  These 2-loop corrections have already been made available in
\softsusy~3.7.0 \cite{Allanach:2014nba}.  The 2-loop \SQCD
corrections of $O(\as^2)$ are now also incorporated in \fstwo and can be
used by setting the following switch in the model file:\footnote{We
  kindly thank Alexander Bednyakov for providing the 2-loop \SQCD
  expressions.}
%
\begin{lstlisting}
UseMSSMYukawa2Loop = True;
\end{lstlisting}
%
To take these 2-loop contributions into account at runtime, the
following flags should also be set in the SLHA input file:
%
\begin{lstlisting}
Block FlexibleSUSY
    7   2         # threshold corrections loop order
   24   122111221 # individual threshold correction loop orders
\end{lstlisting}
%
In \fs's \mathematica interface, the above SLHA configuration options
correspond to
%
\begin{lstlisting}[language=Mathematica]
handle = FS<model>OpenHandle[
    fsSettings -> {thresholdCorrectionsLoopOrder -> 2,
                   thresholdCorrections -> 122111221}
    ...];
\end{lstlisting}
%
In \figref{fig:MSSMMuBMu} we show in blue the effect of the full
2-loop \SQCD corrections on the lightest \CP-even Higgs pole mass in
the MSSM\@.  The blue dashed line shows the effect in \fstwo and the
crosses in \softsusy~4.0.1.
As can be seen from the figure, the full 2-loop \SQCD corrections are
negative and can affect the Higgs mass by several GeV, as has been
observed in Ref.~\cite{Allanach:2014nba}.  In the left panel of
\figref{fig:MSSMMuBMu}, the shift in the Higgs mass is shown as a
function of the SUSY scale.  For scales above $\approx 2\unit{TeV}$ we
find a logarithmic shift in $M_h$, which is caused by new large
logarithms originating from the 2-loop contribution of the SUSY
particles to the \DRbar top Yukawa coupling.  We also find that these
new logarithms alone would spoil the accidental cancellation of large
logarithms described in Ref.~\cite{Athron:2016fuq}.
%
Note that in the MSSM the effect of the 2-loop \SQCD corrections to
the top and bottom Yukawa couplings is a partial 3-loop contribution
to the light \CP-even Higgs pole mass.  Thus, these 2-loop \SQCD corrections
must be taken into account if the explicit 3-loop Higgs mass
contributions of $O(\at \as^2 + \ab \as^2)$ from
\Himalaya are used, see above.
%
\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.49\textwidth]{doc/Manuals/plots/MSSMMuBMu/scan_MSSMMuBMu_Mh_MS_TB-5_Xt-0}\hfill
  \includegraphics[width=0.49\textwidth]{doc/Manuals/plots/MSSMMuBMu/scan_MSSMMuBMu_Mh_Xt_TB-5_MS-2000}
  \caption{Effect of the 3-loop RGEs for all MSSM parameters (red),
    2-loop \SQCD contributions to $y_b$ and $y_t$ (blue) and 2-loop
    \SQCD contributions to $\as$ (green) on the lightest \CP-even
    Higgs pole mass in the MSSM\@.  The lines show the shift in the
    Higgs pole mass in \fstwo compared to the one obtained with 2-loop
    RGEs, full 1-loop \SQCD + 2-loop SM-QCD contributions to $y_t$ and
    1-loop \SQCD contributions to $\as$.  The crosses show the
    corresponding shift obtained with \softsusy~4.0.1.  In the left
    panel we use $\tan\beta = 5$ and $X_t = 0$ and in the right panel
    we fix $\tan\beta = 5$ and $\MS = 2\unit{TeV}$.}
  \label{fig:MSSMMuBMu}
\end{figure}

@@

SUSYScaleInput = {
    {M122, MAInput^2 Sin[ArcTan[v2/v1]] Cos[ArcTan[v2/v1]]},
    FSSolveEWSBFor[EWSBOutputParameters]
};
\end{lstlisting}
%
Finally, we need to fix the quartic Higgs couplings of the \THDMII at
the scale $\MS$.  The necessary relations between the MSSM parameters
and the quartic Higgs couplings of the \THDMII are known at the full
1-loop and leading 2-loop level
\cite{Haber:1993an,Gorbahn:2009pp,Lee:2015uza}.
We can use expressions from these references to write the boundary conditions
on the quartic Higgs couplings at the SUSY scale,
shown in lines 23--57 of \appref{app:THDMIIMSSMBC},
in terms of the 1- and 2-loop threshold corrections,
shown in lines 110--398 of the same listing
which displays the complete
\fs model file.
\figref{fig:THDMIIMSSMBC_Mh_MS} shows the lightest \CP-even
Higgs pole mass calculated at the 1-loop level with \fs in this EFT
setup as a function of $\tan\beta^{\THDMII}(M_t)$ and $\MS$ for
$m_A^{\THDMII}(\MEWSB) = 200\unit{GeV}$, $\MEWSB = M_t$ and maximal
stop mixing.  The figure shows that using this setup, \fs can reproduce
the results presented in the left panels of Figure~2 of
Ref.~\cite{Lee:2015uza}.  This EFT model is
distributed with the \fs package under the name \modelname{THDMIIMSSMBC}.
%
\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.49\textwidth]{doc/Manuals/plots/THDMIIMSSMBC/THDMIIMSSMBC_Mh_MS_TB_MA-200_Xt-0}\hfill
  \includegraphics[width=0.49\textwidth]{doc/Manuals/plots/THDMIIMSSMBC/THDMIIMSSMBC_Mh_MS_TB_MA-200_Xt-sqrt6}
  \caption{Lightest \CP-even Higgs pole mass calculated at the 1-loop
    level in the effective \THDM setup as a function of $\tan\beta$ and
    $\MS$ for $m_A(M_t) = 200\unit{GeV}$, $A_t = \mu/\tan\beta +
    X_t$, $A_b = A_\tau = A_t$, $\mu = \MS$, $M_t = 173.34\unit{GeV}$
    and $\as^{\SM(5)}(M_Z) = 0.1184$.  The left panel shows the results for $X_t
    = 0$ and the right panel for $X_t = \sqrt{6}\MS$.  The solid line
    corresponds to a Higgs pole mass of $125\unit{GeV}$ and the dashed
    lines to $124\unit{GeV}$ and $126\unit{GeV}$, respectively.}
  \label{fig:THDMIIMSSMBC_Mh_MS}
\end{figure}

@@

...
\end{lstlisting}
%
The full expressions for the threshold corrections can be found in the
\HSSUSY model file.  In addition, \HSSUSY makes use of the known
3-loop SM $\beta$ functions, 3-loop corrections to the
running top Yukawa coupling, 3-loop threshold corrections to the
strong coupling and up to 3-loop corrections to the Higgs pole mass:
%
\begin{lstlisting}
UseSM3LoopRGEs    = True; (* 3-loop RGEs *)
UseYukawa3LoopQCD = True; (* 3-loop thresholds for yt *)
UseSMAlphaS3Loop  = True; (* 3-loop thresholds for alpha_s *)
UseHiggs2LoopSM   = True; (* 2-loop contributions to Mh *)
UseHiggs3LoopSM   = True; (* 3-loop contributions to Mh *)
\end{lstlisting}
%
With all these corrections enabled, \HSSUSY can be regarded as an
improved variant of \susyhd \cite{Vega:2015fna}, the difference being
that \HSSUSY includes generalized 2-loop threshold corrections also
involving $\ab$ and $\atau$, which are not present in \susyhd.  In
\secref{sec:feft}, \HSSUSY is also compared to the fixed-order
calculation in the full MSSM as well as to \feft.  The following
Examples \ref{ex:HSSUSY_parallel}--\ref{ex:HSSUSY_EFT_uncertainty}
show how \HSSUSY can be run and how different sources of uncertainty
can be estimated.\footnote{The example scripts can be found in the
  \code{examples-2.0/} sub-directory of the \fs package.}
%
\begin{example}[label=ex:HSSUSY_parallel]
  For illustration, we show in this example the Higgs mass prediction
  in the MSSM with \HSSUSY.  In the following example script, a scan
  over the relative \DRbar stop mixing parameter $X_t/\MS$ is performed for
  $\tan\beta(\MS) = 5$ and three different values of the SUSY scale $\MS$.
  This is done in parallel on all available CPU cores.
  %
\begin{lstlisting}
Get["models/HSSUSY/HSSUSY_librarylink.m"];

@@

data = {
    ParallelMap[{#, CalcMh[5, #, 1000 ]}&, Range[-3.5, 3.5, 0.1]],
    ParallelMap[{#, CalcMh[5, #, 2000 ]}&, Range[-3.5, 3.5, 0.1]],
    ParallelMap[{#, CalcMh[5, #, 10000]}&, Range[-3.5, 3.5, 0.1]]
};
\end{lstlisting}%$
%
When plotting this data, the following figure results:
%
\begin{center}
  \includegraphics[width=0.5\textwidth]{doc/Manuals/plots/HSSUSY/Mh_Xt}
\end{center}
\end{example}

@@

data = {
    ParallelMap[{#, CalcDMh[1000 , 5, #]}&, Range[-3.5, 3.5, 0.1]],
    ParallelMap[{#, CalcDMh[2000 , 5, #]}&, Range[-3.5, 3.5, 0.1]],
    ParallelMap[{#, CalcDMh[10000, 5, #]}&, Range[-3.5, 3.5, 0.1]]
};
\end{lstlisting}%$
%
In the function \code{CalcDMh[]}, the three sources of uncertainty are
combined linearly.  When drawing the uncertainty $\Delta
M_h^{\SM}$, estimated in this way, around the central value as $M_h
\pm \Delta M_h^{\SM}$, the following figure results:
\begin{center}
  \includegraphics[width=0.5\textwidth]{doc/Manuals/plots/HSSUSY/Mh_Xt_uncertainty}
\end{center}
%
We find that the uncertainty $\Delta
M_h^{\SM}$ is around or below $500\unit{MeV}$.
\end{example}

@@

data = ParallelMap[{#, Sequence @@ CalcDMh[#, 5, Sqrt[6]]}&,
                   LogRange[173.34, 10^5, 60]];
\end{lstlisting}%$
%
In the function \code{CalcDMh[]}, the difference between the Higgs masses
calculated with $\texttt{DeltaEFT} = 0$ and $\texttt{DeltaEFT} =
1$ is used as the uncertainty estimate ($\texttt{DeltaEFT} =
0$ corresponds to the standard \HSSUSY calculation).  When drawing the
uncertainty estimated in this way symmetrically around the central
value, the following figure results:
%
\begin{center}
  \includegraphics[width=0.5\textwidth]{doc/Manuals/plots/HSSUSY/Mh_MS_EFT_uncertainty}
\end{center}
%
As expected, we find that the ``EFT uncertainty'' decreases as
$\MS$ increases and falls below $150\unit{MeV}$ for $\MS \gtrsim 2\unit{TeV}$.
\end{example}

@@

    doc/Manuals/plots/CMSSM_solution_regions/CMSSM_solution_regions}

@@

    doc/Manuals/plots/CMSSM_solution_regions/CMSSM_higgs_mass}
